Plotly in Shiny
========================================================

Shiny is an R library to create web applications with your data. If you have never used it before you should read RStudio’s tutorial here: http://shiny.rstudio.com/

We will start with a basic example of Plotly in Shiny using group checkbox, and ggplot’s “iris” dataset.

```{r}
summary(iris)
```

Our ui.R file:

```{r, eval=FALSE}
library("shiny")
shinyUI(
  pageWithSidebar(
    
    headerPanel(title=HTML("Plotly in Shiny"), windowTitle="Plotly in Shiny"),
    
    sidebarPanel(
      checkboxGroupInput(inputId="check_group", # ID to be used in server.R
                         label="Select species:",
                         choices=list("Setosa"="setosa", # Make sure not to mix names with values
                                      "Versicolor"="versicolor",
                                      "Virginica"="virginica"),
                         selected=list("setosa", "versicolor", "virginica"))
      ),
    
    mainPanel(
      htmlOutput("plot") # Argument name from server.R
      )
    ))
```

Remember to add commas after sidebarPanel() and headerPanel(). 
For more information on checkboxGroupInput() click here: http://shiny.rstudio.com/reference/shiny/latest/checkboxGroupInput.html

Our server.R:

```{r, eval=FALSE}
library("shiny") # Load libraries we will be using
library("plotly")
library("ggplot2")

shinyServer(function(input, output) {
  output$plot <- renderUI({ # "plot" to be used as argument in server.R
    
    subset_iris <- iris[iris$Species %in% input$check_group, ] # Subset dataset, using "check_group" argument from server.R
    ggiris <- qplot(x=Petal.Width, y=Sepal.Length, data=subset_iris, color=Species)
    
    py <- plotly(username="pdespouy", key="rl18kwjamr") # Open Plotly connection
    
    res <- py$ggplotly(ggiris, kwargs=list(filename="Plotly in Shiny", 
                                           fileopt="overwrite", # Overwrite plot in Plotly's website
                                           auto_open=FALSE))
    
    tags$iframe(src=res$response$url,
                frameBorder="0", # Some aesthetics
                height=400,
                width=650)
  })
})
```

For more informaiton on tags$iframe() click here: http://shiny.rstudio.com/articles/tag-glossary.html

Then after you make sure ui.R and server.R are in the same folder (and working directory), run on your console:

```{r, eval=FALSE}
runApp()
```

And voilà, a Shiny app using Plotly!

<iframe src="http://pedrodz.shinyapps.io/shiny_example/" width="1000" height="500" frameBorder="0"></iframe>
